Outbreak Threshold Detection

### 2023-08-16 notebooks/Julia/simulation-detection.qmd
Rename gamma vars for clarity

μ = 1
beta = 1000
sigma = 365/8
γ = 365/5
ε = 100
p = (beta, sigma, γ, μ, ε)
```

@@

recov_rate(u, p, t) = p[3] * u[3]   # γ * I
function recov_affect!(integrator)
    integrator.u[3] -= 1         # I -> I - 1
    integrator.u[4] += 1         # R -> R + 1
    nothing
end
recov_jump = ConstantRateJump(recov_rate, recov_affect!)

>>>>

μ = 1
beta = 1000
sigma = 365/8
gamma = 365/5
ε = 100
p = (beta, sigma, gamma, μ, ε)
```

@@

recov_rate(u, p, t) = p[3] * u[3]   # gamma * I
function recov_affect!(integrator)
    integrator.u[3] -= 1         # I -> I - 1
    integrator.u[4] += 1         # R -> R + 1
    nothing
end
recov_jump = ConstantRateJump(recov_rate, recov_affect!)
